Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-07 doc/slides/hong+eisner.TLT13.slides.tex
updated the motivation. There is an ILP section still left TODO. But the rough draft of the presentation is mostly covered.

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item We need a multiheaded dependency corpus for parsing
  \end{itemize}
}

>>>>

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for building new parsers
  \end{itemize}
}

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
  \end{itemize}
}

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item We explored whether the Link Grammar could be adapted for this purpose.
  \end{itemize}
}

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item We explored whether the Link Grammar could be adapted for this purpose.
    \item The results of this are mixed, but provides a good case study.
  \end{itemize}
}
